### 2020-08-25 paper/perfectGraphs.tex
Near cleaner proof

@@

	Let $R(x_1, y_1) = p_1-\ldots -p_n$, and let $R(x_2, y_1) = q_1-\ldots -q_{n+1}$, where $p_1 = x_1$, $p_n = q_{n+1} = y_1$, $q_1 = x_2$ and $q_n = y_2$. From the definition of $R(x_1, y_1)$ and $R(x_2, y_1)$, none of $p_2, \ldots, p_{n-1}, q_2, \ldots, q_n$ belong to $X$. Also, from the definition of $y_1$, $y_1 \notin X$.
\end{proof}

>>>>

\begin{wrapfigure}{r}{0.35\textwidth}
	\input{tikzpictures/nearCleanerFound.tex}
	\caption{An odd hole is found}%
	\vspace{-0.5cm}
\end{wrapfigure}

@@

	Let $R(x_1, y_1) = p_1-\ldots -p_n$, and let $R(x_2, y_1) = q_1-\ldots -q_{n+1}$, where $p_1 = x_1$, $p_n = q_{n+1} = y_1$, $q_1 = x_2$ and $q_n = y_2$. From the definition of $R(x_1, y_1)$ and $R(x_2, y_1)$, none of $p_2, \ldots, p_{n-1}, q_2, \ldots, q_n$ belong to $X$. Also, from the definition of $y_1$, $y_1 \notin X$.

	Since $r(x_1, y_1) = r(x_2, y_1) - 1$ and since $x_1$, $x_2$ are nonadjacent it follows that $x_2$ does not belong to $R(x_1, y_1)$ and $x_1$ does not belong to $R(x_2, y_1)$. Since $r(x_3, y_1), r(x_3, y_2) \geq n (= r(x_1, y_2))$ it follows that $x_3$ does not belong to $R(x_1, y_1)$ or to $R(x_2, y_1)$, and has no neighbors in $R(x_1, y_1) \cup R(x_2, y_1)$ other than $x_1$, $x_2$. Since $r(x_1, y_2) = n$ we get that $y_2$ does not belong to $R(x_1, y_1)$.

	We claim first that the insides of paths $R(x_1, y_1)$ and $R(x_2, y_1)$ have no common vertices. For suppose that there are $2 \leq i \leq n-1$ and $2 \leq j \leq n$ that $p_i = q_j$. Then the subpaths of these two paths between $p_i$, $y_1$ are both subpaths of the shortest paths, and therefore have the same length, that is $j=i+1$. So $p_1-\ldots-p_1-q_{j+1}-\ldots-q_n$ contains a path between $x_1$, $y_2$ of length $\leq n-2$, contradicting that $r(x_1, y_2) = n$. So $R(x_1, y_1)$ and $R(x_2, y_1)$ have no common vertex except $y_1$.

	If there are no edges between $R(x_1, y_1) \setminus y_1$ and $R(x_2, y_1) \setminus y_1$ then the union of these two paths and a path $x_1-x_3-x_2$ form an odd hole, so the answer is correct.

	Suppose that $p_iq_j$ is an edge for some $1\leq i \leq n-1$ and $1 \leq j \leq n$. We claim $i \geq j$. If $j = 1$ this is clear so let us assume $j > 1$. Then there is a path between $x_1$, $y_2$ within $\{p_1, \ldots , p_i, q_j, \ldots q_n\}$ which has length $\leq n-j+1$ and has no internal vertex in $X$ (since $j > 1$); and since $r(x_1, y_2) = n$, it follows that $n-j+i \geq n$, that is, $i \geq j$ as claimed.

	Now, since $x_1$, $x_2$ are nonadjacent $i \geq 2$. But also $r(x_2, y_1) \geq n$ and so $j+n-i \geq n$, that is $j \geq i$. So we get $i=j$. Let us choose $i$ minumum, then $x_3-x_1-\ldots-p_i-q_i-\ldots-x_2-x_3$ is an odd hole, which was what we wanted.
\end{proof}
